Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
small pass over infrastructure

\paragraph{The Dune build system~\cite{dune}}
This build system, originally written for OCaml, but that was extended to support Coq projects, allows building packages contained in a single source tree separately, which is essential to be able to publish the different libraries contained in a single repository as separate (opam) packages to the Coq package index.

@@

\paragraph{The Docker-Coq-Action~\cite{martindorel2020dockercoq}}
This GitHub Action provides a very simple way of setting up Continuous Integration (CI) for a Coq project with an opam file.
%
At the current time, we rely on it, together with the mathcomp Docker images~\cite{mathcompdocker}, to test our two main libraries, Hydra-battles and Addition-chains, with multiple versions of Coq.

\paragraph{The Coq Nix Toolbox~\cite{cohen:hal-03366644}}
This toolbox, based on the Nix package manager, provides an alternative way of setting up CI for a Coq project (also relying on GitHub Actions).
%
We use this Nix-based CI for several things.

>>>>

\paragraph{The Dune build system~\cite{dune}.}
Dune was originally designed to build OCaml projects, but was recently extended to support Coq. Dune allows building packages contained in a single source tree separately, which is essential to be able to publish the different libraries contained in a single repository as separate (opam) packages to the Coq package index.

@@

\paragraph{The Docker-Coq-Action~\cite{martindorel2020dockercoq}.}
This GitHub Action provides a very simple way of setting up Continuous Integration (CI) for a Coq project with an opam file.
%
At the current time, we rely on it, together with the mathcomp Docker images~\cite{mathcompdocker}, to test our two main libraries, Hydra-battles and Addition-chains, with multiple versions of Coq.

\paragraph{The Coq Nix Toolbox~\cite{cohen:hal-03366644}.}
This toolbox, based on the Nix package manager, provides an alternative way of setting up CI for a Coq project (also relying on GitHub Actions).
%
We use this Nix-based CI for several things.
